### 2024-05-08 thesis/sections/6.1-object-identification.tex
language analysis

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-2}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {100}                         & {100}     & {2} & {10}  & {99,96\%}                           \\
        {100}                         & {1000}    & {2} & {10}  & {99,96\%}                           \\
        {1000}                        & {100}     & {3} & {10}  & {99,87\%}                           \\
        {500}                         & {100}     & {3} & {100} & {99,83\%}                           \\
        {100}                         & {100}     & {6} & {50}  & {99,83\%}                           \\
        {100}                         & {500}     & {3} & {16}  & {99,7\%}                            \\
        {1000}                        & {100}     & {6} & {16}  & {99,61\%}                           \\
        {100}                         & {100}     & {6} & {100} & {99,57\%}                           \\
        {100}                         & {500}     & {1} & {100} & {99,52\%}                           \\
        {100}                         & {100}     & {1} & {50}  & {99,35\%}                           \\
        {500}                         & {100}     & {1} & {2}   & {99,26\%}                           \\
        {100}                         & {500}     & {1} & {50}  & {99,26\%}                           \\
        {500}                         & {500}     & {1} & {100} & {99,26\%}                           \\
        {100}                         & {500}     & {3} & {100} & {99,83\%}                           \\
        {500}                         & {1000}    & {1} & {16}  & {98\%}                              \\
        {100}                         & {500}     & {1} & {10}  & {96,61\%}                           \\
        {100}                         & {1000}    & {1} & {100} & {99,44\%}                           \\
        {500}                         & {500}     & {6} & {2}   & {95,92\%}                           \\
        {100}                         & {1000}    & {4} & {2}   & {94,88\%}                           \\
        {100}                         & {1000}    & {6} & {10}  & \textcolor{purple}{63,15\%}         \\
        {1000}                        & {500}     & {2} & {2}   & \textcolor{purple}{62,98\%}         \\\midrule
        \multicolumn{4}{c|}{baseline} & {62,72\%}                                                     \\\midrule
        {100}                         & {1000}    & {3} & {2}   & \textcolor{purple}{61,2\%}          \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'Dale-2' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_dale-2}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-5}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {1000}                        & {500}     & {3} & {50}  & {91,75\%}                           \\
        {100}                         & {100}     & {6} & {10}  & {91,02\%}                           \\
        {100}                         & {100}     & {3} & {10}  & {90,76\%}                           \\
        {100}                         & {100}     & {4} & {16}  & {89,76\%}                           \\
        {100}                         & {100}     & {2} & {10}  & {88,85\%}                           \\
        {500}                         & {1000}    & {1} & {100} & {87,11\%}                           \\
        {1000}                        & {1000}    & {6} & {50}  & {85,07\%}                           \\
        {500}                         & {1000}    & {1} & {10}  & {84,46\%}                           \\
        {500}                         & {500}     & {1} & {50}  & {83,29\%}                           \\
        {100}                         & {100}     & {1} & {10}  & {80,86\%}                           \\
        {500}                         & {100}     & {1} & {100} & {76,74\%}                           \\
        {500}                         & {500}     & {4} & {2}   & {77,78\%}                           \\
        {1000}                        & {1000}    & {3} & {2}   & {75,78\%}                           \\
        {100}                         & {100}     & {3} & {2}   & {74\%}                              \\
        {500}                         & {500}     & {1} & {2}   & {63,41\%}                           \\\midrule
        \multicolumn{4}{c|}{baseline} & {35,07\%}                                                     \\\midrule
        {500}                         & {1000}    & {2} & {100} & \textcolor{purple}{34,98\%}         \\
        {500}                         & {500}     & {3} & {16}  & \textcolor{purple}{34,77\%}         \\
        {500}                         & {500}     & {6} & {2}   & \textcolor{purple}{34,38\%}         \\
        {1000}                        & {1000}    & {4} & {2}   & \textcolor{purple}{35,33\%}         \\
        {1000}                        & {1000}    & {6} & {100} & \textcolor{purple}{35,24\%}         \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'Dale-5' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_dale-5}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{CLEVR color}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                        \\\midrule
        {100}                         & {1000}    & {3} & {10}  & {73,65\%}                                \\
        {100}                         & {1000}    & {3} & {16}  & {73,57\%}                                \\
        {500}                         & {500}     & {4} & {10}  & {73,57\%}                                \\
        {100}                         & {500}     & {3} & {16}  & {70,75\%}                                \\
        {100}                         & {1000}    & {4} & {50}  & {69,31\%}                                \\
        {1000}                        & {500}     & {1} & {16}  & {62,85\%}                                \\
        {100}                         & {500}     & {1} & {10}  & {57,12\%}                                \\
        {1000}                        & {500}     & {6} & {16}  & {54,69\%}                                \\
        {100}                         & {100}     & {4} & {2}   & {52,95\%}                                \\
        {1000}                        & {500}     & {1} & {100} & {52,82\%}                                \\
        {100}                         & {1000}    & {1} & {100} & {52,34\%}                                \\
        {100}                         & {500}     & {3} & {2}   & {51,48\%}                                \\
        {500}                         & {1000}    & {3} & {16}  & \textcolor{purple}{24,61\%}              \\
        {100}                         & {1000}    & {3} & {50}  & \textcolor{purple}{24,48\%}              \\
        {1000}                        & {1000}    & {4} & {100} & \textcolor{purple}{24\%}                 \\
        {500}                         & {1000}    & {1} & {2}   & \textcolor{purple}{23,96\%}              \\
        {1000}                        & {100}     & {6} & {10}  & \textcolor{purple}{23,87\%}              \\
        {500}                         & {1000}    & {6} & {50}  & \textcolor{purple}{23,87\%}              \\\midrule
        \multicolumn{4}{c|}{baseline} & {23,74\%}                                                          \\\midrule
        {500}                         & {500}     & {2} & {2}   & \textcolor{purple}{22,35\%}              \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'CLEVR color' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_color}
\end{table}

>>>>

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-2}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {100}                         & {100}     & {2} & {10}  & {99,96\%}                           \\
        {100}                         & {1000}    & {2} & {10}  & {99,96\%}                           \\
        {1000}                        & {100}     & {3} & {10}  & {99,87\%}                           \\
        {500}                         & {100}     & {3} & {100} & {99,83\%}                           \\
        {100}                         & {100}     & {6} & {50}  & {99,83\%}                           \\
        {100}                         & {500}     & {3} & {16}  & {99,7\%}                            \\
        {1000}                        & {100}     & {6} & {16}  & {99,61\%}                           \\
        {100}                         & {100}     & {6} & {100} & {99,57\%}                           \\
        {100}                         & {500}     & {1} & {100} & {99,52\%}                           \\
        {100}                         & {100}     & {1} & {50}  & {99,35\%}                           \\
        {500}                         & {100}     & {1} & {2}   & {99,26\%}                           \\
        {100}                         & {500}     & {1} & {50}  & {99,26\%}                           \\
        {500}                         & {500}     & {1} & {100} & {99,26\%}                           \\
        {100}                         & {500}     & {3} & {100} & {99,83\%}                           \\
        {500}                         & {1000}    & {1} & {16}  & {98\%}                              \\
        {100}                         & {500}     & {1} & {10}  & {96,61\%}                           \\
        {100}                         & {1000}    & {1} & {100} & {99,44\%}                           \\
        {500}                         & {500}     & {6} & {2}   & {95,92\%}                           \\
        {100}                         & {1000}    & {4} & {2}   & {94,88\%}                           \\
        {100}                         & {1000}    & {6} & {10}  & \textcolor{red}{63,15\%}            \\
        {1000}                        & {500}     & {2} & {2}   & \textcolor{red}{62,98\%}            \\\midrule
        \multicolumn{4}{c|}{baseline} & {62,72\%}                                                     \\\midrule
        {100}                         & {1000}    & {3} & {2}   & \textcolor{red}{61,2\%}             \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'Dale-2' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_dale-2}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{Dale-5}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                   \\\midrule
        {1000}                        & {500}     & {3} & {50}  & {91,75\%}                           \\
        {100}                         & {100}     & {6} & {10}  & {91,02\%}                           \\
        {100}                         & {100}     & {3} & {10}  & {90,76\%}                           \\
        {100}                         & {100}     & {4} & {16}  & {89,76\%}                           \\
        {100}                         & {100}     & {2} & {10}  & {88,85\%}                           \\
        {500}                         & {1000}    & {1} & {100} & {87,11\%}                           \\
        {1000}                        & {1000}    & {6} & {50}  & {85,07\%}                           \\
        {500}                         & {1000}    & {1} & {10}  & {84,46\%}                           \\
        {500}                         & {500}     & {1} & {50}  & {83,29\%}                           \\
        {100}                         & {100}     & {1} & {10}  & {80,86\%}                           \\
        {500}                         & {100}     & {1} & {100} & {76,74\%}                           \\
        {500}                         & {500}     & {4} & {2}   & {77,78\%}                           \\
        {1000}                        & {1000}    & {3} & {2}   & {75,78\%}                           \\
        {100}                         & {100}     & {3} & {2}   & {74\%}                              \\
        {500}                         & {500}     & {1} & {2}   & {63,41\%}                           \\\midrule
        \multicolumn{4}{c|}{baseline} & {35,07\%}                                                     \\\midrule
        {500}                         & {1000}    & {2} & {100} & \textcolor{red}{34,98\%}            \\
        {500}                         & {500}     & {3} & {16}  & \textcolor{red}{34,77\%}            \\
        {500}                         & {500}     & {6} & {2}   & \textcolor{red}{34,38\%}            \\
        {1000}                        & {1000}    & {4} & {2}   & \textcolor{red}{35,33\%}            \\
        {1000}                        & {1000}    & {6} & {100} & \textcolor{red}{35,24\%}            \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'Dale-5' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_dale-5}
\end{table}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{cccc|c}
        \toprule
                                      &           &     &       & \multicolumn{1}{c}{\textbf{CLEVR color}} \\  \cmidrule(lr){5-5}
        $h_r$                         & $h_s$     & $n$ & $|V|$ & \textbf{Accuracy}                        \\\midrule
        {100}                         & {1000}    & {3} & {10}  & {73,65\%}                                \\
        {100}                         & {1000}    & {3} & {16}  & {73,57\%}                                \\
        {500}                         & {500}     & {4} & {10}  & {73,57\%}                                \\
        {100}                         & {500}     & {3} & {16}  & {70,75\%}                                \\
        {100}                         & {1000}    & {4} & {50}  & {69,31\%}                                \\
        {1000}                        & {500}     & {1} & {16}  & {62,85\%}                                \\
        {100}                         & {500}     & {1} & {10}  & {57,12\%}                                \\
        {1000}                        & {500}     & {6} & {16}  & {54,69\%}                                \\
        {100}                         & {100}     & {4} & {2}   & {52,95\%}                                \\
        {1000}                        & {500}     & {1} & {100} & {52,82\%}                                \\
        {100}                         & {1000}    & {1} & {100} & {52,34\%}                                \\
        {100}                         & {500}     & {3} & {2}   & {51,48\%}                                \\
        {500}                         & {1000}    & {3} & {16}  & \textcolor{red}{24,61\%}                 \\
        {100}                         & {1000}    & {3} & {50}  & \textcolor{red}{24,48\%}                 \\
        {1000}                        & {1000}    & {4} & {100} & \textcolor{red}{24\%}                    \\
        {500}                         & {1000}    & {1} & {2}   & \textcolor{red}{23,96\%}                 \\
        {1000}                        & {100}     & {6} & {10}  & \textcolor{red}{23,87\%}                 \\
        {500}                         & {1000}    & {6} & {50}  & \textcolor{red}{23,87\%}                 \\\midrule
        \multicolumn{4}{c|}{baseline} & {23,74\%}                                                          \\\midrule
        {500}                         & {500}     & {2} & {2}   & \textcolor{red}{22,35\%}                 \\
        \bottomrule
    \end{tabular}
    \caption{Selected results of the object identification games on the 'CLEVR color' dataset with $e_s=100$ and $e_r=500$ after 128.000 games}
    \label{tab:results_discriminator_color}
\end{table}
